---
title: "Untitled"
author: "Ross"
date: "02/07/2018"
output: 
  slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

l <- function() {
  paste0('
<slide class="" id="">
<hgroup>

</hgroup>
<article>

<footer class = "logo">
<div style="position: absolute; left: 1500px; top: 0px; z-index:100">
<img src = "imgs/YSI.png" height="80" width="80">
</div>
</footer>
</article>
</slide>
')
}

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

`r l()`

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

`r l()`

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

`r l()`

## Slide with Plot

```{r pressure}
plot(pressure)


```

`r l()`